### 2017-03-16 readme.Rmd
readme updates
update to readme

$\lambda(z) = \tilde \lambda(z) \cdot s(z)$

@@

#now let's try and select a few key layers.
```{r,eval=FALSE}
tassie_preds <- stack(tas_climate[[1]],tas_climate[[5]],tas_climate[[6]],
  tas_climate[[12]],tas_climate[[14]],tas_pop,tas_dist_from_roads)
names(tassie_preds)<-c("annual_mean_temperature","annual_precipitation","max_temperature_of_warmest_month","min_temperature_of_coldest_month","precipitation_of_driest_month","human_population_density","distance_from_main_roads")
writeRaster(tassie_preds, filename="./data_files/tassie_predictors.tif", options="INTERLEAVE=BAND", overwrite=TRUE)
```

@@

$pr(y=0) = exp(-s(z)*A) $

@@

$pr( y=1) = 1-pr(y=0) $
         $= 1-exp(-s(z)*A) $

@@

$\lambda(x)= e^{\tilde \alpha + \tilde\beta^\prime x_1(z)} e^{\gamma^\prime + \delta x_2(x)}$

@@

par(mfrow=c(1,2),oma=c(4,4,4,4))
plot(p_v_lampra_w_s_cell,col=jet.colors(100),main='accounting for sighting bias')
points(po_v_lampra,pch=16,cex=0.4,col=rgb(0, 0, 0, 0.3))
plot(p_v_lampra_wo_s_cell,col=jet.colors(100),main='ignoring sighting bias')
points(po_v_lampra,pch=16,cex=0.4,col=rgb(0, 0, 0, 0.3))

>>>>

$$\lambda(z) = \tilde \lambda(z) \cdot s(z)$$

@@

Now let's try and select a few key layers.
```{r,eval=FALSE}
tassie_preds <- stack(tas_climate[[1]],tas_climate[[5]],tas_climate[[6]],
  tas_climate[[12]],tas_climate[[14]],tas_pop,tas_dist_from_roads)
names(tassie_preds)<-c("annual_mean_temperature","annual_precipitation","max_temperature_of_warmest_month","min_temperature_of_coldest_month","precipitation_of_driest_month","human_population_density","distance_from_main_roads")
writeRaster(tassie_preds, filename="./data_files/tassie_predictors.tif", options="INTERLEAVE=BAND", overwrite=TRUE)
```

@@

$$pr(y=0) = exp(-s(z)*A)$$

@@

$$pr( y=1) = 1-pr(y=0)$$
         $$= 1-exp(-s(z)*A)$$

@@

$$\lambda(x)= e^{\tilde \alpha + \tilde\beta^\prime x_1(z)} e^{\gamma^\prime + \delta x_2(x)}$$

@@

par(mfrow=c(1,2),oma=c(4,4,4,4))
plot(p_v_lampra_w_s_cell,col=jet.colors(100),main='accounting for sighting bias',
  xlim=c(144.5, 148.5), ylim=c(-43.8,-40.5))
points(po_v_lampra,pch=16,cex=0.4,col=rgb(0, 0, 0, 0.3))
plot(p_v_lampra_wo_s_cell,col=jet.colors(100),main='ignoring sighting bias',
  xlim=c(144.5, 148.5), ylim=c(-43.8,-40.5))
points(po_v_lampra,pch=16,cex=0.4,col=rgb(0, 0, 0, 0.3))
